---
title: "Exercise1"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Exploratory analysis: green buildings

An Austin real-estate developer is interested in the possible economic impact of "going green" in her latest project: a new 15-story mixed-use building on East Cesar Chavez, just across I-35 from downtown. Will investing in a green building be worth it, from an economic perspective? The baseline construction costs are $100 million, with a 5% expected premium for green certification.

Do you agree with the conclusions of her on-staff stats guru? If so, point to evidence supporting his case. If not, explain specifically where and why the analysis goes wrong, and how it can be improved.

```{r cars}
library(mosaic)
green = read.csv('greenbuildings.csv')
green = subset(green, leasing_rate >= 10)
summary(green)
```

What effect rent?
```{r}
lm.fit.green = lm(Rent~., data = green)
summary(lm.fit.green)
```

```{r}
green_only = subset(green, green_rating==1)
non_green = subset(green, green_rating==0)
```
```{r}
# How does siz effect rant?
median(green$size)
median(non_green$size)
median(green_only$size)
green_only_15 = subset(green_only, stories == 15)
median(green_only_15$size)
```
```{r}
plot(Rent ~ size, data=green, pch=19, cex=0.5, col='brown')
abline(lm(green$Rent~green$size))
abline(v=median(green_only$size), col='red')
abline(v=median(green_only_15$size), col='red')
#figure out how much difference is from green and size. Use multiple variable regression, build trunks
```
```{r}
#How does the employment growth rate effect rent?
plot(Rent ~ empl_gr, data=green, pch=19, cex=0.5, col='brown')
```
```{r}
#Leasing rate
median(green$leasing_rate)
median(non_green$leasing_rate)
median(green_only$leasing_rate)
green_only_15 = subset(green_only, stories == 15)
median(green_only_15$leasing_rate)
```

```{r}
#stories
plot(Rent ~ stories, data=green, pch=19, cex=0.5, col='brown')
abline(lm(green$Rent~green$stories))
abline(v=11, col='red')
abline(v=15, col='red')
```
```{r}
median(green$stories)
median(non_green$stories)
median(green_only$stories)
#green_only_15 = subset(green_only, stories == 15)
#median(green_only_15$leasing_rate)
```
```{r}
#age
plot(Rent ~ age, data=green, pch=19, cex=0.5, col='brown')
abline(lm(green$Rent~green$age))
```
```{r}
median(green$age)
median(non_green$age)
median(green_only$age)
median(subset(green_only, stories == 15)$age)
```
```{r}
# class
class=ifelse(green$class_a == 1 ,"a",ifelse(green$class_b == 1 ,"b","c"))
green_2 =data.frame(green,class)
bwplot(Rent ~ class, data=green_2)
#abline(lm(green$Rent~green$age))
```
```{r}
table1=xtabs(~green_rating + class, data=green)
prop.table(table1, margin=1)
```
```{r}
#net
median(subset(green_only, net == 1)$Rent)
median(subset(green_only, net == 0)$Rent)
```
```{r}
table1=xtabs(~green_rating + net, data=green)
prop.table(table1, margin=1)
```
```{r}
#amenities
median(subset(green, amenities == 1)$Rent)
median(subset(green, amenities == 0)$Rent)
```

```{r}
#hd_total07
plot(Rent ~ hd_total07, data=green, pch=19, cex=0.5, col='brown')
abline(lm(green$Rent~green$hd_total07))#?
```
```{r}
mean(green$hd_total07)
mean(non_green$hd_total07)
mean(green_only$hd_total07)
mean(subset(green_only, stories == 15)$hd_total07)
```
```{r}
#Precipitation
plot(Rent ~ Precipitation, data=green, pch=19, cex=0.5, col='brown')
abline(lm(green$Rent~green$Precipitation))
```
```{r}
mean(green$Precipitation)
mean(non_green$Precipitation)
mean(green_only$Precipitation)
mean(subset(green_only, stories == 15)$Precipitation)
```
```{r}
#Gas_Costs
plot(Rent ~ Gas_Costs, data=green, pch=19, cex=0.5, col='brown')
abline(lm(non_green$Rent~non_green$Gas_Costs))
abline(lm(green_only$Rent~green_only$Gas_Costs),col='blue')
```
```{r}
#Electricity_Costs
plot(Rent ~ Electricity_Costs, data=green, pch=19, cex=0.5, col='brown')
abline(lm(non_green$Rent~non_green$Electricity_Costs))
abline(lm(green_only$Rent~green_only$Electricity_Costs),col='blue')
```
```{r}
#cluster_rent
plot(Rent ~ cluster_rent, data=green, pch=19, cex=0.5, col='brown')
abline(lm(non_green$Rent~non_green$cluster_rent))
abline(lm(green_only$Rent~green_only$cluster_rent),col='blue')
```



## Bootstrapping

1.marshals appropriate evidence to characterize the risk/return properties of the five major asset classes listed above.
```{r}
library(mosaic)
library(quantmod)
library(foreach)
mystocks = c("SPY", "TLT", "LQD", "EEM", "VNQ")
myprices = getSymbols(mystocks, from = "2007-01-01")
```
```{r}
for(ticker in mystocks) {
	expr = paste0(ticker, "a = adjustOHLC(", ticker, ")")
	eval(parse(text=expr))
}
head(SPYa)
```
```{r}
plot(ClCl(SPYa))
```
```{r}
plot(ClCl(TLTa))
```
```{r}
plot(ClCl(LQDa))
```
```{r}
plot(ClCl(EEMa))
```
2008.7 EEM reduce the stork volume and the price increased three times.
```{r}
plot(ClCl(VNQa))
```
```{r}
all_returns = cbind(	ClCl(SPYa),
								ClCl(TLTa),
								ClCl(LQDa),
								ClCl(EEMa),
								ClCl(VNQa))
head(all_returns)
all_returns = as.matrix(na.omit(all_returns))
```
```{r}
pairs(all_returns)
```

2. outlines your choice of the "safe" and "aggressive" portfolios.
    a. the even split: 20% of your assets in each of the five ETFs above.
    b. something that seems safer than the even split, comprising investments in at least three classes. 
    c. something more aggressive  comprising investments in at least two classes/assets. 
```{r}
my_weights1 = c(0.2,0.2,0.2, 0.2, 0.2)
my_weights2 = c(0.1,0.4,0.4, 0.1, 0.0)
my_weights3 = c(0.4,0.0,0.0, 0.2, 0.4)
```

3.uses bootstrap resampling to estimate the 4-week (20 trading day) value at risk of each of your three portfolios at the 5% level.

```{r}
#even split
set.seed(1)
sim1 = foreach(i=1:5000, .combine='rbind') %do% {
  total_wealth = 100000
  holdings1 = my_weights1 * total_wealth
  n_days = 20
  wealthtracker1 = rep(0, n_days) 
  for(today in 1:n_days) {
  	return.today = resample(all_returns, 1, orig.ids=FALSE)
  	holdings1 = holdings1 + holdings1*return.today
	  total_wealth1 = sum(holdings1)
	  wealthtracker1[today] = total_wealth1
  	holdings1 = my_weights1 * total_wealth1 #reblance the acounts after daily growth
  }
  wealthtracker1
}
head(sim1)
hist(sim1[,n_days], 25)
```
```{r}
mean(sim1[,n_days])
sqrt(var(sim1[,n_days]))
hist(sim1[,n_days]- 100000, breaks=30)
quantile(sim1[,n_days], 0.05) - 100000
```

```{r}
#safe portfolio
set.seed(1)
sim2 = foreach(i=1:5000, .combine='rbind') %do% {
  total_wealth = 100000
  holdings2 = my_weights2 * total_wealth
  n_days = 20
  wealthtracker2 = rep(0, n_days) 
  for(today in 1:n_days) {
    #set.seed(1)
	  return.today = resample(all_returns, 1, orig.ids=FALSE)
	  holdings2 = holdings2 + holdings2*return.today
	  total_wealth2 = sum(holdings2)
	  wealthtracker2[today] = total_wealth2
	  holdings2 = my_weights2 * total_wealth2 #reblance the acounts after daily growth
  }
  wealthtracker2
}
#total_wealth
#plot(wealthtracker2, type='l')
head(sim2)
hist(sim2[,n_days], 25)
```
```{r}
mean(sim2[,n_days])
sqrt(var(sim2[,n_days]))
hist(sim2[,n_days]- 100000, breaks=30)
quantile(sim2[,n_days], 0.05) - 100000
```
```{r}
#aggrasive portfolio
set.seed(1)
sim3 = foreach(i=1:5000, .combine='rbind') %do% {
  total_wealth = 100000
  holdings3 = my_weights3 * total_wealth
  n_days = 20
  wealthtracker3 = rep(0, n_days) 
  for(today in 1:n_days) {
	  return.today = resample(all_returns, 1, orig.ids=FALSE)
	  holdings3 = holdings3 + holdings3*return.today
	  total_wealth3 = sum(holdings3)
	  wealthtracker3[today] = total_wealth3
	  holdings3 = my_weights3 * total_wealth3 #reblance the acounts after daily growth
  }
  wealthtracker3
}
#total_wealth
#plot(wealthtracker2, type='l')
head(sim3)
hist(sim3[,n_days], 25)
```
```{r}
mean(sim3[,n_days])
sqrt(var(sim3[,n_days]))
hist(sim3[,n_days]- 100000, breaks=30)
quantile(sim3[,n_days], 0.05) - 100000
```

3.compares the results for each portfolio in a way that would allow the reader to make an intelligent decision among the three options.

## Market segmentation


















